Do we need detailed demographic data to forecast plant population responses to climate change?

### 2015-06-16 manuscript/manuscript.Rmd
fixes some more typos

@@

colnames(stats_table) <- c("Species", "Model", "MAE", "90% Distance", "Mean Obs. Cover")
print.xtable(xtable(stats_table, caption = "Accuracy (mean absoluet error, MAE) and precision (90\\% Distance) of out of sample predictions. Forecasts were made without random year effects; only climate covariates could explain year-to-year variation. 90\\% Distance refers to the average distance between the upper and lower 90th percentiles of the 100 predicted values for each quadrat-year combination."),type="latex", comment=FALSE,
             include.rownames=FALSE, caption.placement="top")
```
*NOTES*: The IPM MAE is significantly lower at $\alpha=0.05$ for *B. gracilis* (*P* = `r mae_ps[1,"value"]`), *H. comata* (*P* = `r mae_ps[2,"value"]`), and *P. smithii* (*P* = `r mae_ps[3,"value"]`). MAEs are statisticially similar between models for *P. secunda* (*P* = `r mae_ps[4,"value"]`).

>>>>

Acknowledgments
---------------
This work was funded by the National Science Foundation through a Postdoctoral Research Fellowship in Biology to ATT (DBI-1400370) and a CAREER award to PBA (DEB-1054040). We thank the original mappers of the permanent quadrats in Montana and the digitizers in the Adler lab, without whom this work would not have been possible. Informal conversations with Stephen Ellner, Giles Hooker, Robin Snyder, and a series of meetings among the Adler and Weecology labs at USU sharpened our thinking.

@@

colnames(stats_table) <- c("Species", "Model", "MAE", "90% Distance", "Mean Obs. Cover")
print.xtable(xtable(stats_table, caption = "Accuracy (mean absolute error, MAE) and precision (90\\% Distance) of out of sample predictions. Forecasts were made without random year effects; only climate covariates could explain year-to-year variation. 90\\% Distance refers to the average distance between the upper and lower 90th percentiles of the 100 predicted values for each quadrat-year combination."),type="latex", comment=FALSE,
             include.rownames=FALSE, caption.placement="top")
```
*NOTES*: The IPM MAE is significantly lower at $\alpha=0.05$ for *B. gracilis* (*P* = `r mae_ps[1,"value"]`), *H. comata* (*P* = `r mae_ps[2,"value"]`), and *P. smithii* (*P* = `r mae_ps[3,"value"]`). MAEs are statisticially similar between models for *P. secunda* (*P* = `r mae_ps[4,"value"]`).

### 2015-06-16 manuscript/manuscript.tex
fixes some more typos

Our main goal in this paper is to see if models based on aggregate level
data are as sensitive to climate as models based on individual level
data. So, with our fitted and validated models in hand, we ran
simulations for each model type (IPM and QBM) under four climate
perturbation scenarios: (1) observed climate, (2) precipitation
increased by 1\%, (3) temperature increased by 1\%, and (4)
precipitation and temperature increased by 1\%. We ran this simulations
for 2,500 time steps, enough to estimate equilibrium cover after
discarding an initial 500 time steps as burn-in. Each simulation was run
under two parameter scenarios: (1) using mean parameter estimates and
(2) using randomly drawn parameters from the MCMC chain. We use (1) to
detect the overall sensitivity of equilibrium cover to climate, and we
use (2) to show the impact of model uncertainty on forecast precision.

@@

>>>>

Our main goal in this paper is to see if models based on aggregate level
data are as sensitive to climate as models based on individual level
data. So, with our fitted and validated models in hand, we ran
simulations for each model type (IPM and QBM) under four climate
perturbation scenarios: (1) observed climate, (2) precipitation
increased by 1\%, (3) temperature increased by 1\%, and (4)
precipitation and temperature increased by 1\%. We ran the simulations
for 2,500 time steps, enough to estimate equilibrium cover after
discarding an initial 500 time steps as burn-in. Each simulation was run
under two parameter scenarios: (1) using mean parameter estimates and
(2) using randomly drawn parameters from the MCMC chain. We use (1) to
detect the overall sensitivity of equilibrium cover to climate, and we
use (2) to show the impact of model uncertainty on forecast precision.

@@

\subsection{Acknowledgments}\label{acknowledgments}

This work was funded by the National Science Foundation through a
Postdoctoral Research Fellowship in Biology to ATT (DBI-1400370) and a
CAREER award to PBA (DEB-1054040). We thank the original mappers of the
permanent quadrats in Montana and the digitizers in the Adler lab,
without whom this work would not have been possible. Informal
conversations with Stephen Ellner, Giles Hooker, Robin Snyder, and a
series of meetings among the Adler and Weecology labs at USU sharpened
our thinking.
